Exposure Consequences - Statistics and Figures

### 2018-01-22 ManuscriptMaterials.Rmd
updated reach aftereffect plot to use all data for panel B (and for the comparison between classic and exposure too)

```{r fig.width=10, fig.height=4}
plotReachAftereffects()
```

@@

First, we show that no-cursor reaches change direction after exposure training:

@@

Let's minimize the potential explanatory power of the target by removing it from the model:

@@

This doesn't seem to change anything, so that whether or not we account for any effects of target direction, there is no overall effect of training with volitional movements (classic) or passive movements (exposure) on -- the amplitude of -- reach aftereffects.

>>>>

```{r fig.width=7.5, fig.height=4}
plotReachAftereffects()
```

_For Panel B: Earlier I used the initial block for this plot, but after discussion, we decided to use all data: there's no significant difference between the initial and other blocks, but using all data allows more accurate estimates._

@@

First, we show that no-cursor reaches change direction immediately after exposure training (iteration 1):

@@

The absence of an interaction between training and target could be interpreted to mean that the generalization of reach aftereffects is the same after both kinds of training. Here are the confidence intervals for both:

```{r}
cat('\nCLASSIC\n\n')
getPeakConfidenceInterval('classic',part='all',CIs=c(.95))
cat('\nEXPOSURE\n\n')
getPeakConfidenceInterval('exposure',part='all',CIs=c(.95))
```

Although the two peaks are not different from each other, the 95% confidence interval for the classically trained group includes the 45 degree target (where the visual feedback was during training), whereas the 95% confidence interval for the exposure training group includes the 75 degree target (where the hand really was during training). So something might be going on -- but the evidence is far from concrete.

Let's go back to seeing if there is any effect from training type on reach aftereffects at all, and minimize the potential explanatory power of target by removing it from the model:

@@

This doesn't seem to change one iota, so that whether or not we account for any effects of target direction, there is no overall effect of training with volitional movements (classic) or passive movements (exposure) on -- the amplitude of -- reach aftereffects.
